Synthesising Complex Termination Arguments

### 2014-06-23 papers/termination/paper.tex
Move GF(2^k) to footnote

As well as machine arithmetic differing from Peano arithmetic on the operators they have in common,
computers have several ``bitwise'' operations that are not taken as primitive in the theory of
integers.  These operations include the standard boolean operations \texttt{and, or, not, xor}
applied to each element of the bit-vector.  Computer programs often make use of these operators,
which are non-linear when interpreted in the standard model of Peano arithmetic
(although some of these operators can be seen as linear in a different algebraic structure,
e.g. \texttt{xor} corresponds to addition in the Galois field $\mathrm{GF}(2^k)$).

>>>>

As well as machine arithmetic differing from Peano arithmetic on the operators they have in common,
computers have several ``bitwise'' operations that are not taken as primitive in the theory of
integers.  These operations include the standard boolean operations \texttt{and, or, not, xor}
applied to each element of the bit-vector.  Computer programs often make use of these operators,
which are non-linear when interpreted in the standard model of Peano arithmetic\footnote{
Although some of these operators can be seen as linear in a different algebraic structure,
e.g. \texttt{xor} corresponds to addition in the Galois field $\mathrm{GF}(2^k)$}.
